---
title: "Norrköping PLFA Analyses"
author: "Andreas Schneider"
date: "2024-04"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    number_sections: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

suppressMessages({
  library(here)
  library(readxl)
  library(ggplot2)
  library(agricolae)
  library(gridExtra)
  library(ggsignif)
  library(rcartocolor)
})

```

# Import data

```{r}
plfa_all <- read_excel(here("21115_PLFA_NorrköpingRosinedal.xlsx"), sheet = 2)[,-c(3,29)]

plfa_all$dataset <- ifelse(grepl("R18", plfa_all$`ID 2`), "Rosinedal", "Norrköping")

plfa_all_num <- data.matrix(plfa_all[,c(3:27)])
```

Now we also import metadat and merge it with the PLFA data.

```{r}
plfa_all2 <- as.data.frame(plfa_all_num)

#REMOVE AFTER MISTAKE HAS BEEN FIXED
rownames(plfa_all2) <- plfa_all$`ID 2`
plfa_n <- plfa_all2[!grepl("R18", rownames(plfa_all2)),]

#Import meta
trans <- readRDS(here("doc/Soil_data_clean.rds"))
meta <- readRDS(here("doc/meta_soil.rds"))

###############SETUP MERGE
plfa_n2 <- data.frame(Cust_ID_1=rownames(plfa_n), plfa_n)
plfa_n3 <- merge.data.frame(plfa_n2, trans, by = "Cust_ID_1")
plfa_n3 <- plfa_n3[,c(1:27)]
plfa_n4 <- merge.data.frame(plfa_n3, meta)



```

# Principal Component analysis

Then we can start with a PCA of the data

```{r}
#Start with PCA
pca_n <- prcomp(data.matrix(plfa_n4[3:27]))
percent_n <- round(summary(pca_n)$importance[2,]*100, digits = 1)
comps_n <- as.data.frame(pca_n$x[, 1:3])
rownames(comps_n) <- plfa_n4$SampleID_sum

comps_n <- cbind(comps_n, plfa_n4[,c(28:34)])

ggplot(comps_n, aes(x = PC1, y = PC2))+
  geom_point(size = 3, aes(col = Planting_Position))+
  xlab(paste0("PC1 [", percent_n[1], "%]"))+
  ylab(paste0("PC2 [", percent_n[2], "%]"))+
  scale_fill_manual(values = c("darkred", "darkblue"))+
  theme_minimal()
```

# Statistical tests and boxplots 

```{r}
##Make boxplots of bacterial and fungal biomass split by planting position and year (control)

bacterial_list <- c("i.14.0", "i.15.0", "a.15.0", "X15.0", "i.16.0", "X10Me16.0", "i.17.0", "a.17.0", "cy17.0", 
                    "X17.0", "X10Me17.0", "X18.1w7", "X10Me18.0", "cy19.0")

plfa_n4_data <- data.matrix(plfa_n4[,3:27])
rownames(plfa_n4_data) <- plfa_n4$SampleID_sum
plfa_n4_data_df <- as.data.frame(plfa_n4_data)

plfa_n4_meta <- plfa_n4[,c(1,28:34)]
rownames(plfa_n4_meta) <- plfa_n4_meta$SampleID_sum

## Summarise into three columns (Fungi, Bacteria, all PLFAs)
plfa_rel <- data.frame(SampleID_sum=rownames(plfa_n4_data_df),
                       Fungi=plfa_n4_data_df$X18.2w6.9, 
                       Bacteria=rowSums(plfa_n4_data_df[,bacterial_list]),
                       F_B_ratio=plfa_n4_data_df$X18.2w6.9/rowSums(plfa_n4_data_df[,bacterial_list]),
                       All=rowSums(plfa_n4_data_df))

#### Check the edges
edges <- plfa_n4_meta$SampleID_sum[grepl("Edge", plfa_n4_meta$Block)]
plfa_rel_e <- plfa_rel[edges,]
plfa_n4_meta_e <- plfa_n4_meta[edges,]

##Kruskal

kruskal(plfa_rel_e$Fungi, plfa_n4_meta_e$Type, console = T, p.adj = "fdr")
kruskal(plfa_rel_e$Fungi, plfa_n4_meta_e$Planting_Position, console = T, p.adj = "fdr")
kruskal(plfa_rel_e$Fungi, paste0(plfa_n4_meta_e$Planting_Position, plfa_n4_meta_e$Type), console = T, p.adj = "fdr")

```

```{r}
plfa_rel_e2 <- merge.data.frame(plfa_rel_e, plfa_n4_meta_e, by = "SampleID_sum")

p1=ggplot(plfa_rel_e2, aes(x = Planting_Position, y = Bacteria))+
  geom_boxplot(aes(fill=Planting_Position))+
  facet_wrap(~Type)+
  theme_minimal()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle=90))
p2=ggplot(plfa_rel_e2, aes(x = Planting_Position, y = Fungi))+
  geom_boxplot(aes(fill=Planting_Position))+
  facet_wrap(~Type)+
  theme_minimal()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle=90))

p3=ggplot(plfa_rel_e2, aes(x = Planting_Position, y = F_B_ratio))+
  geom_boxplot(aes(fill=Planting_Position))+
  facet_wrap(~Type)+
  theme_minimal()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle=90))

p4=ggplot(plfa_rel_e2, aes(x = Planting_Position, y = All))+
  geom_boxplot(aes(fill=Planting_Position))+
  facet_wrap(~Type)+
  theme_minimal()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle=90))

grid.arrange(p1, p2, p3, p4, nrow = 1)

ggplot(plfa_rel_e2, aes(x = Planting_Position, y = Fungi))+
  geom_boxplot(aes(fill=Planting_Position))+
  facet_wrap(~Type)+
  theme_minimal()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle=90))


kruskal.test(plfa_rel_e2$Fungi, plfa_rel_e2$Type)
```

# Plot for Fig S2

```{r}
##Plot for Fig S2
ggplot(plfa_rel_e2, aes(x = Type, y = Fungi))+
  geom_boxplot(aes(fill = Type), outlier.shape = NA)+
  geom_jitter(aes(col = Planting_Position), size = 2, alpha = 0.6, width = 0.15)+
  geom_signif(
    comparisons = list(c("Soil_CC", "Soil_Forest")),
    map_signif_level = TRUE
  )+
  scale_fill_manual(values = alpha(c("sienna4", "springgreen4"), 0.3))+
  scale_y_continuous(name=expression(paste("PLFA 18:2ω6,9 in nmol ", g^-1, " dw of soil")))+
  scale_x_discrete(labels=c("Soil_CC"="Clear-cut", "Soil_Forest"="Forest"), name=element_blank())+
  scale_color_discrete(name="Location")+
  theme_light()
```

# Control Block Soil only

```{r}
#########################Control block soil
control_soil_block <- plfa_n4_meta$SampleID_sum[grepl("Soil_Block", plfa_n4_meta$Type) 
                                                & plfa_n4_meta$Treatment=="Control"
                                                & !is.na(plfa_n4_meta$Treatment)]

meta_csb <- plfa_n4_meta[control_soil_block,]
plfa_rel_csb <- plfa_rel[control_soil_block,]

#Difference between blocks?
###POINTLESS, since in this part there is only one replicate per block!
#adonis(soil_all_r_csb$omegaC_Perc ~ meta_csb$Block)
#adonis(soil_all_r_csb$omegaN_Perc ~ meta_csb$Block)
#adonis(soil_all_r_csb$C_N_ratio ~ meta_csb$Block)
#Plot:
plfa_rel_csb2 <- merge.data.frame(plfa_rel_csb, meta_csb)
pb_1 <- ggplot(plfa_rel_csb2, aes(x = Planting_Position, y = Bacteria))+
  geom_boxplot(aes(fill=Planting_Position))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "Earth", direction = 1)+
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.x = element_blank())

pb_2 <- ggplot(plfa_rel_csb2, aes(x = Planting_Position, y = Fungi))+
  geom_boxplot(aes(fill=Planting_Position))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "Earth", direction = 1)+
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.x = element_blank())

pb_3 <- ggplot(plfa_rel_csb2, aes(x = Planting_Position, y = F_B_ratio))+
  geom_boxplot(aes(fill=Planting_Position))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "Earth", direction = 1)+
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.x = element_blank())

pb_4 <- ggplot(plfa_rel_csb2, aes(x = Planting_Position, y = All))+
  geom_boxplot(aes(fill=Planting_Position))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "Earth", direction = 1)+
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.x = element_blank())

grid.arrange(pb_1, pb_2, pb_3, pb_4, nrow = 1)
```

# Fig S9 Spruce

```{r}
### FOR FIG S9


#KRUSKAL
#Species, PP, Year
set.seed(555)
kruskal(plfa_rel_csb$Fungi, meta_csb$Species, console = T, p.adj = "fdr")
kruskal(plfa_rel_csb$Fungi, meta_csb$Planting_Position, console = T, p.adj = "fdr")
kruskal(plfa_rel_csb$Fungi, meta_csb$Year, console = T, p.adj = "fdr")
kruskal(plfa_rel_csb$Fungi, paste0(meta_csb$Species,meta_csb$Planting_Position,meta_csb$Year), console = T, p.adj = "fdr")
kruskal(plfa_rel_csb$Fungi, paste0(meta_csb$Species,meta_csb$Planting_Position), console = T, p.adj = "fdr")


#Take all control soil samples (block and rhizosphere)
control_soil_all <- plfa_n4_meta$SampleID_sum[grepl("Soil_Block|Soil_Rhizo", plfa_n4_meta$Type) 
                                                & plfa_n4_meta$Treatment=="Control"
                                                & !is.na(plfa_n4_meta$Treatment)]

meta_csa <- plfa_n4_meta[control_soil_all,]
plfa_rel_csa <- plfa_rel[control_soil_all,]

#######################BOXPLOT FOR FIG S9
plfa_rel_csa_all <- merge.data.frame(plfa_rel_csa, meta_csa)
plfa_rel_csa_all$Type <- factor(plfa_rel_csa_all$Type, levels = rev(unique(plfa_rel_csa_all$Type)))
plfa_rel_csa_all$Planting_Position <- factor(plfa_rel_csa_all$Planting_Position, levels = unique(plfa_rel_csa_all$Planting_Position))
####E; SPRUCE
plfa_rel_csa_all_sp <- plfa_rel_csa_all[plfa_rel_csa_all$Species=="Spruce",]
plfa_rel_csa_all_sp_2017 <- plfa_rel_csa_all_sp[plfa_rel_csa_all_sp$Year=="2017",]
plfa_rel_csa_all_sp_2018 <- plfa_rel_csa_all_sp[plfa_rel_csa_all_sp$Year=="2018",]

kruskal(plfa_rel_csa_all_sp_2017$Fungi, paste0(plfa_rel_csa_all_sp_2017$Type, plfa_rel_csa_all_sp_2017$Planting_Position), console = T, p.adj = "fdr")
kruskal(plfa_rel_csa_all_sp_2018$Fungi, paste0(plfa_rel_csa_all_sp_2018$Type, plfa_rel_csa_all_sp_2018$Planting_Position), console = T, p.adj = "fdr")

ggplot(plfa_rel_csa_all_sp, aes(x = Type, y = Fungi))+
  geom_boxplot(aes(fill=Planting_Position))+
  facet_wrap(~Year)+
  scale_y_continuous(name=expression(paste("PLFA 18:2ω6,9 in nmol ", g^-1, " dw of soil")))+
  scale_x_discrete(labels=c("Soil_Block"="Bulk", "Soil_Rhizo"="Rhizosphere"), name=element_blank())+
  scale_fill_carto_d(palette = "Earth", direction = -1)+
  theme_light()+
  theme(legend.position = "none",
        axis.title.x = element_blank())
```

# Fig S9 Pine

```{r}
####F; PINE
plfa_rel_csa_all_pi <- plfa_rel_csa_all[plfa_rel_csa_all$Species=="Pine",]
plfa_rel_csa_all_pi_2017 <- plfa_rel_csa_all_pi[plfa_rel_csa_all_pi$Year=="2017",]
plfa_rel_csa_all_pi_2018 <- plfa_rel_csa_all_pi[plfa_rel_csa_all_pi$Year=="2018",]

kruskal(plfa_rel_csa_all_pi_2017$Fungi, paste0(plfa_rel_csa_all_pi_2017$Type, plfa_rel_csa_all_pi_2017$Planting_Position), console = T, p.adj = "fdr")
kruskal(plfa_rel_csa_all_pi_2018$Fungi, paste0(plfa_rel_csa_all_pi_2018$Type, plfa_rel_csa_all_pi_2018$Planting_Position), console = T, p.adj = "fdr")


ggplot(plfa_rel_csa_all_pi, aes(x = Type, y = Fungi))+
  geom_boxplot(aes(fill=Planting_Position))+
  facet_wrap(~Year)+
  scale_y_continuous(name=expression(paste("PLFA 18:2ω6,9 in nmol ", g^-1, " dw of soil")))+
  scale_x_discrete(labels=c("Soil_Block"="Bulk", "Soil_Rhizo"="Rhizosphere"), name=element_blank())+
  scale_fill_carto_d(palette = "Earth", direction = -1)+
  theme_light()+
  theme(legend.position = "none",
        axis.title.x = element_blank())
```


```{r}
kruskal(plfa_rel_csa_all_pi$Fungi, plfa_rel_csa_all_pi$Planting_Position, console = T, p.adj = "fdr")
#Both
kruskal(plfa_rel_csa_all$Fungi, plfa_rel_csa_all$Planting_Position, console = T, p.adj = "fdr")

##2017
plfa_rel_csa_all_2017 <- plfa_rel_csa_all[plfa_rel_csa_all$Year=="2017",]
kruskal(plfa_rel_csa_all_2017$Fungi, plfa_rel_csa_all_2017$Type, console = T, p.adj = "fdr")
```

# Separate by Planting Position

## Capped Mounds

```{r}
#Separate by planting position
meta_csa_cm <- meta_csa[grepl("Capped", meta_csa$Planting_Position),]
meta_csa_bm <- meta_csa[grepl("Mineral", meta_csa$Planting_Position),]

plfa_rel_csa_cm <- plfa_rel_csa[grepl("Capped", meta_csa$Planting_Position),]  
plfa_rel_csa_bm <- plfa_rel_csa[grepl("Mineral", meta_csa$Planting_Position),]

###Capped Mounds
plfa_rel_csa_cm2 <- merge.data.frame(plfa_rel_csa_cm, meta_csa_cm)
pb_cm_1 <- ggplot(plfa_rel_csa_cm2, aes(x = Planting_Position, y = Bacteria))+
  geom_boxplot(aes(fill=Type))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "ArmyRose", direction = 1)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())

pb_cm_2 <- ggplot(plfa_rel_csa_cm2, aes(x = Planting_Position, y = Fungi))+
  geom_boxplot(aes(fill=Type))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "ArmyRose", direction = 1)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())

pb_cm_3 <- ggplot(plfa_rel_csa_cm2, aes(x = Planting_Position, y = F_B_ratio))+
  geom_boxplot(aes(fill=Type))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "ArmyRose", direction = 1)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())

pb_cm_4 <- ggplot(plfa_rel_csa_cm2, aes(x = Planting_Position, y = All))+
  geom_boxplot(aes(fill=Type))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "ArmyRose", direction = 1)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())

grid.arrange(pb_cm_1, pb_cm_2, pb_cm_3, pb_cm_4, nrow = 2)
```

## Mineral soils

```{r}
###Mineral soils
plfa_rel_csa_bm2 <- merge.data.frame(plfa_rel_csa_bm, meta_csa_bm)
pb_bm_1 <- ggplot(plfa_rel_csa_bm2, aes(x = Planting_Position, y = Bacteria))+
  geom_boxplot(aes(fill=Type))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "ArmyRose", direction = 1)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())

pb_bm_2 <- ggplot(plfa_rel_csa_bm2, aes(x = Planting_Position, y = Fungi))+
  geom_boxplot(aes(fill=Type))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "ArmyRose", direction = 1)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())

pb_bm_3 <- ggplot(plfa_rel_csa_bm2, aes(x = Planting_Position, y = F_B_ratio))+
  geom_boxplot(aes(fill=Type))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "ArmyRose", direction = 1)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())

pb_bm_4 <- ggplot(plfa_rel_csa_bm2, aes(x = Planting_Position, y = All))+
  geom_boxplot(aes(fill=Type))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "ArmyRose", direction = 1)+
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())

grid.arrange(pb_bm_1, pb_bm_2, pb_bm_3, pb_bm_4, nrow = 2)
```

# Norway spruce mineral soil 2018 vs 2017

```{r}
plfa_rel_csa_bm2_sp <- plfa_rel_csa_bm2[plfa_rel_csa_bm2$Species=="Spruce",]

kruskal(plfa_rel_csa_bm2_sp$Fungi, plfa_rel_csa_bm2_sp$Year, p.adj = "fdr", console = T)
```

```{r}
plfa_rel_csa2 <- plfa_rel_csa
plfa_rel_csa2 <- merge.data.frame(plfa_rel_csa2, meta_csa, by = "SampleID_sum")
```


# Treatment effect on rhizosphere soils

```{r}
# Treatment rhizosphere
rhizosphere <- plfa_n4_meta$SampleID_sum[grepl("Soil_Rhizo", plfa_n4_meta$Type) 
                                              & !is.na(plfa_n4_meta$Treatment)]

meta_rhiz <- plfa_n4_meta[rhizosphere,]
plfa_rel_rhiz <- plfa_rel[rhizosphere,]



plfa_rel_rhiz2 <- merge.data.frame(plfa_rel_rhiz, meta_rhiz)
pb_rh_1 <- ggplot(plfa_rel_rhiz2, aes(x = Planting_Position, y = Bacteria))+
  geom_boxplot(aes(fill=Treatment))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "ArmyRose", direction = 1)+
  theme(axis.title.x = element_blank())

pb_rh_2 <- ggplot(plfa_rel_rhiz2, aes(x = Planting_Position, y = Fungi))+
  geom_boxplot(aes(fill=Treatment))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "ArmyRose", direction = 1)+
  theme(axis.title.x = element_blank())

pb_rh_3 <- ggplot(plfa_rel_rhiz2, aes(x = Planting_Position, y = F_B_ratio))+
  geom_boxplot(aes(fill=Treatment))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "ArmyRose", direction = 1)+
  theme(axis.title.x = element_blank())

pb_rh_4 <- ggplot(plfa_rel_rhiz2, aes(x = Planting_Position, y = All))+
  geom_boxplot(aes(fill=Treatment))+
  facet_wrap(~Species+Year)+
  theme_minimal()+
  scale_fill_carto_d(palette = "ArmyRose", direction = 1)+
  theme(axis.title.x = element_blank())

grid.arrange(pb_rh_1, pb_rh_2, pb_rh_3, pb_rh_4, nrow = 2)
```

# Fig S12

## Spruce

```{r}

plfa_rel_rhiz2_spr_min <- plfa_rel_rhiz2[plfa_rel_rhiz2$Species=="Spruce"&plfa_rel_rhiz2$Planting_Position=="Exposed_Mineral",]

###Separate Spruce and Pine for Fig S12

plfa_rel_rhiz2$Treatment <- factor(plfa_rel_rhiz2$Treatment, levels=c("Control", "Argrow", "Osmocote"))
plfa_rel_rhiz2$Planting_Position <- factor(plfa_rel_rhiz2$Planting_Position, levels = c("Exposed_Mineral", "Capped_Mound"))

#Spruce, A
plfa_rel_rhiz2_sp <- plfa_rel_rhiz2[plfa_rel_rhiz2$Species=="Spruce",]

#Stats
plfa_rel_rhiz2_sp_2017 <- plfa_rel_rhiz2_sp[plfa_rel_rhiz2_sp$Year=="2017",]
plfa_rel_rhiz2_sp_2018 <- plfa_rel_rhiz2_sp[plfa_rel_rhiz2_sp$Year=="2018",]

kruskal(plfa_rel_rhiz2_sp_2017$Fungi, paste0(plfa_rel_rhiz2_sp_2017$Planting_Position, plfa_rel_rhiz2_sp_2017$Treatment), console = T, p.adj = "fdr")
kruskal(plfa_rel_rhiz2_sp_2018$Fungi, paste0(plfa_rel_rhiz2_sp_2018$Planting_Position, plfa_rel_rhiz2_sp_2018$Treatment), console = T, p.adj = "fdr")


ggplot(plfa_rel_rhiz2_sp, aes(x = Planting_Position, y = Fungi))+
  geom_boxplot(aes(fill=Treatment))+
  facet_wrap(~Year)+
  scale_fill_carto_d(palette = "TealGrn")+
  scale_y_continuous(name=expression(paste("PLFA 18:2ω6,9 in nmol ", g^-1, " dw of soil")))+
  scale_x_discrete(labels=c("Exposed_Mineral"="Exposed\nMineral", "Capped_Mound"="Capped\nMound"), name=element_blank())+
  theme_light()+
  theme(axis.title.x = element_blank(),
        legend.position = "none")
```


### Statistical comparisons

```{r}
kruskal(plfa_rel_rhiz2_sp$Fungi, plfa_rel_rhiz2_sp$Planting_Position, p.adj = "fdr", console = T)
kruskal(plfa_rel_rhiz2_sp$F_B_ratio, plfa_rel_rhiz2_sp$Planting_Position, p.adj = "fdr", console = T)
kruskal(plfa_rel_rhiz2_sp$All, plfa_rel_rhiz2_sp$Planting_Position, p.adj = "fdr", console = T)

kruskal(plfa_rel_rhiz2_sp$Fungi, plfa_rel_rhiz2_sp$Treatment, p.adj = "fdr", console = T)
kruskal(plfa_rel_rhiz2_sp$F_B_ratio, plfa_rel_rhiz2_sp$Treatment, p.adj = "fdr", console = T)
kruskal(plfa_rel_rhiz2_sp$All, plfa_rel_rhiz2_sp$Treatment, p.adj = "fdr", console = T)

kruskal(plfa_rel_rhiz2_sp$Fungi, plfa_rel_rhiz2_sp$Year, p.adj = "fdr", console = T)
kruskal(plfa_rel_rhiz2_sp$F_B_ratio, plfa_rel_rhiz2_sp$Year, p.adj = "fdr", console = T)
kruskal(plfa_rel_rhiz2_sp$All, plfa_rel_rhiz2_sp$Year, p.adj = "fdr", console = T)
```

## Scots Pine

```{r}
#Pine, B
plfa_rel_rhiz2_pi <- plfa_rel_rhiz2[plfa_rel_rhiz2$Species=="Pine",]

#Stats
plfa_rel_rhiz2_pi_2017 <- plfa_rel_rhiz2_pi[plfa_rel_rhiz2_pi$Year=="2017",]
plfa_rel_rhiz2_pi_2018 <- plfa_rel_rhiz2_pi[plfa_rel_rhiz2_pi$Year=="2018",]

kruskal(plfa_rel_rhiz2_pi_2017$Fungi, paste0(plfa_rel_rhiz2_pi_2017$Planting_Position, plfa_rel_rhiz2_pi_2017$Treatment), console = T, p.adj = "fdr")
kruskal(plfa_rel_rhiz2_pi_2018$Fungi, paste0(plfa_rel_rhiz2_pi_2018$Planting_Position, plfa_rel_rhiz2_pi_2018$Treatment), console = T, p.adj = "fdr")


ggplot(plfa_rel_rhiz2_pi, aes(x = Planting_Position, y = Fungi))+
  geom_boxplot(aes(fill=Treatment))+
  facet_wrap(~Year)+
  scale_fill_carto_d(palette = "TealGrn")+
  scale_y_continuous(name=expression(paste("PLFA 18:2ω6,9 in nmol ", g^-1, " dw of soil")))+
  scale_x_discrete(labels=c("Exposed_Mineral"="Exposed\nMineral", "Capped_Mound"="Capped\nMound"), name=element_blank())+
  theme_light()+
  theme(axis.title.x = element_blank(),
        legend.position = "none")
```

### Statistical comparisons

```{r}
kruskal(plfa_rel_rhiz2_pi$Fungi, plfa_rel_rhiz2_pi$Planting_Position, p.adj = "fdr", console = T)
kruskal(plfa_rel_rhiz2_pi$F_B_ratio, plfa_rel_rhiz2_pi$Planting_Position, p.adj = "fdr", console = T)
kruskal(plfa_rel_rhiz2_pi$All, plfa_rel_rhiz2_pi$Planting_Position, p.adj = "fdr", console = T)

kruskal(plfa_rel_rhiz2_pi$Fungi, plfa_rel_rhiz2_pi$Treatment, p.adj = "fdr", console = T)
kruskal(plfa_rel_rhiz2_pi$F_B_ratio, plfa_rel_rhiz2_pi$Treatment, p.adj = "fdr", console = T)
kruskal(plfa_rel_rhiz2_pi$All, plfa_rel_rhiz2_pi$Treatment, p.adj = "fdr", console = T)

kruskal(plfa_rel_rhiz2_pi$Fungi, plfa_rel_rhiz2_pi$Year, p.adj = "fdr", console = T)
kruskal(plfa_rel_rhiz2_pi$F_B_ratio, plfa_rel_rhiz2_pi$Year, p.adj = "fdr", console = T)
kruskal(plfa_rel_rhiz2_pi$All, plfa_rel_rhiz2_pi$Year, p.adj = "fdr", console = T)
```

